---
title: "Leaflet Project"
author: "Daniel Veit"
date: "5/11/2022"
output: html_document
---

## **Objective**
Create a web page using R Markdown that features a map created with Leaflet. 
Host your webpage on either GitHub Pages, RPubs, or NeoCities.
Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

## **Load Required Packages**
```{r}
suppressMessages(library(leaflet))
suppressMessages(library(dplyr))
```

## **Load the Data**
Data includes a list of the casualties count in battles in world history. The list includes both sieges (not technically battles but usually yielding similar combat-related deaths) and civilian casualties during the battles.
```{r}
sieges <- read.csv("sieges.csv",header=TRUE)
```

## **Clean Data**
```{r}
data <- data.frame(Sieges=sieges$Siege,
                   Casulties=sieges$Casualties,
                   Year=sieges$Year,
                   lat=sieges$lat,
                   long=sieges$lon)
```

## **Activating Map**
```{r, message=FALSE}
map <- data %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup=paste
             (sieges$Siege,
              "<br>Year: ",sieges$Year,
              "<br>Casulties: ",sieges$Casualties))
map
```

